---
output:
  bookdown::pdf_book:
    toc_depth: 2
    fig_height : 5
    fig_width : 8
    citation_package: natbib
    includes:
      in_header: import.sty 
      before_body: title.sty
documentclass: report
classoption : oneside
bibliography: references.bib
csl: ama.csl
geometry: [top=1in, bottom=1in, right=1in, left=1.5in]
linestretch: 2
fontsize: 12pt
---
\pagenumbering{gobble}

\newpage

\listoftables

\listoffigures

\newpage

\pagenumbering{arabic}

```{r, include=FALSE}
knitr :: opts_chunk$set(echo=F, warning=F, message=F, fig.align = 'center',comment=NA)
```

# 

## Introduction:

As a project intern at the International Centre for Diarrheal Disease Research, Bangladesh (ICDDR,B), I was assigned to the study that is the subject of this article. The icddr,b and its goals are briefly described in this chapter. It gives a brief overview of the project's goals and the project to which I was assigned. The exact duties that I was given while working on this project as an intern are also mentioned.


## About icddr,b

The South-East Asia Treaty Organisation (SEATO) Cholera Research Laboratory (icddr,b) was founded in Dhaka in the 1960s.In research on diarrheal diseases, the Cholera Research Laboratory (CRL) quickly gained a reputation on a global scale. The creation, testing, and adoption of oral rehydration solution (ORS), a treatment that is thought to have saved tens of millions of lives globally, was one of its early major accomplishments.The CRL was given a new lease on life in 1978 when it was given the moniker International Centre for Diarrheal Disease Research, Bangladesh. Its sole name in recent years has been icddr,b.In order to address the main public health problems that Bangladesh and other countries in the global South face, icddr,b continued to extend its research. Numerous research initiatives have been carried out in fields like maternal, neonatal, respiratory, and vaccine testing

## Major Achievements

Here’s a brief list of some major achievements of icddr,b:
  
 * Oral Rehydration Solution
 * Zinc Treatment for Diarrhea
 * Tetanus Toxoid Vaccine for Mothers
 * Guidelines for Treating Severe Malnutrition
 * Testing Vaccines
 * Family Planning Solutions
 * Domestic Violence Legislation
 * Mat for Measuring Maternal Blood Loss
 * Ultra Low-cost CPAP(Continuous positive airway pressure therapy) Device for se- vere pneumonia
 * Supplementary and therapeutic foodstuffs to prevent and treat malnutrition


## Internship Goal
Internships are generally thought of to gain experience in a particular field. However, a wide array of people can benefit from Training Internships in order to receive real world experience and develop their skills. Followings are the objectives of my internship:

* Apply statistical knowledge and concepts to real world decision making.
* Increase proficiency in specific statistical disciplines.
* Developandimproveskillsincommunication,quantitativereasoning,andteamwork.
* Meet professional role models and potential mentors who can provide guidance, feedback, and support.
* Expand network of professional relationships and contacts.
* Learn in details about the healthcare facilities of Bangladesh and how they work.
* Develop a solid work ethic and professional demeanor, as well as a commitment to ethical conduct and social responsibility.

##  My Assignmentment

During the internship period I was a member of a team at MCHD department. Our task was to find out if there is any trend in the improved sanitation condition of bangladesh using available BDHS data of 2007 to 2017/18 and also point out the factors behind the trend if any. Following responsibilities were assigned to me as an intern :

* Literature review for analysis 
* Make an analysis plan
* Analyze the descriptive statistics
* Creating dummyt tables 
* Interpret the findings
* Help to write the final report


# 

## Description 

### Introduction 

Pneumonia and serious infections are leading cause of under-five death in Bangladesh. More than 30,000 under-five death are occured due to these reason. WHO recommended to follow Integrated management of childhood illness(IMCI) to manage these serious diseases in outpatient departments. For IMCI, there is a dedicated service register, monthly reporting form and DHIS2 report to track the progress. IMIC guidelines suggests that  child pneumonia and serious infection referred to higher level facilities for indoor management. But there is no dedicated register, monthly reporting form and DHIS2 report in Bangladesh. As a result, taking proper policy becomes difficult. So introducing a standardized register can keep a positive impact here and can be helped to improve skil of healthcare providers.It is important to track management to achieve the SDG target of reducing under-five deaths and neonatal deaths.a national technical committee was formed to develop a standardized register system.The National Newborn Health and IMCI programme helps to demonstrate the inpatient register in selected districts to inform evidence-based scale up.

### Objectives of the study

The objective of the study is to assess the usability, acceptability , adoption , fidelity, utility and impatient register for managing sick newborns and children in selection facilities of Bangladesh.

### Study design 

A research study was conducted where the national newborn health and IMIC programmed designed, developed and demonstrated a standardized impatient for newborn and sick-children.
Icddr,b provided implementation facilitation support and assessments.

### Study setting

The study was conducted in Kushtia and Dinajpur district of Bangladesh. The standardized register was introduced in the pediatric department of district hospitals and all sub-district hospitals of kushtia and Dinajpur district. 

### Introduction of the register

#### Development 

The national newborn health and IMIC programme designed and developed the register system. To do this, a technical committee was formed under leadership of the national newborn health and IMIC programme.The team at first visited one district hospital and one sub district hospital to explore the existing methods / documents practices in the health facilities system and they mainly focus on the pediatric inpatient department. After that, they extract data from the pediatric department to understand the different types of caseloads and their management. 
They also reviewed different national and global guidelines, strategies, case recordings forms and others available there.

Four workshop were organizd by the technical committee to develop the register and they take some decisions from these discussions such as ,
 * Population : under five
 * Cover all diseases but with special focus on pneumonia and serious infection
 * Follow WHO pocket book for hospital care of children
 * The register should allow tracking of use of antibiotics in inpatient department.
 * Use ICD-10 code for diagnosis
 * Develop monthly reporting form based on the register
 * Register to be filled by nurses from case-record forms


#### Implementation

The study is implemented in 
 * District and facility sensitization workshop
 * ToT for doctors 
 * Training of nurses
 * Supply register and reporting forms
 * Monitoring and evaluation 


### Study  participants

In that study, data are collected from sick newborn and under-five children admitted in the pediatric inpatient department. Service providers(doctors and nurses) and their supervisors,
Facility managers, district and sub-district health managers, national level health workers and policy makers.

### Sampling 

Sample size for each of the primary research questions based on the benchmark set of successful demonstration.

### Data collection 

Data is collected from November 2022 to January 2023 (3 months duration).In that data collection process, at first data is collected from under five patients in the pediatric indoor department  by nurse. After that, the nurse of icddr,b also collected data what is called case-recording. Total 11737 data are collected and case-recording data are 5062.

## Analysis

### overall table 


```{r}
library(kableExtra)

collapse_rows_dt <- data.frame(Variable =  c(rep("Age", 5), rep("Sex",4),rep("District",3),rep("Facility type",3), rep("Month",4),rep("Disease",6), rep("Outcome of treatment",6), rep("Missing",1)),
                               Background = c("0-28 days","29-2months","2 months-1year","1 year-5 years","Missing","Male","Female","Others","Missing","Kushtia","Dinajpur","Missing","DH","UHC","Missing","November","December","January","Missing","Newborn Sepsis","Birth Asphyxia","Prematurity and LBW","Severe Pneumonia","Diarrhea","Bronchiolitis","Discharge with advice","Discharge on request","DORB","Refer","Absconded","Death","Missing"),
                              N= c(1320,472,4084,5861,0,6663,4486,26,562,8167,3570,0,604,75690,0,2881,4339,4372,145,59,270,141,1251,4235,661,3982,2529,674,682,956,42,2872),
                              Percentage = c(11.25,4.02,34.8,49.94,0,59.62,40.14,0.23,0,69.58,30.42,0,51.52,48.48,0,24.85,37.43,37.72,0,0.5,2.3,1.2,10.66,16.08,5.63,44.92,28.53,7.6,7.69,10.78,0.47,0))
kbl(collapse_rows_dt,caption = "Overall Background", align = "c") %>%
                                 kable_paper(full_width = F) %>%
                                 column_spec(1, bold = T) %>%
                                 collapse_rows(columns = 1:2, valign = "middle")


```


### Completeness table

```{r}
registration = data.frame(
  
  Variable = c(rep("Facility Type",2), rep("District",2),rep("Month",3), rep("Supervised",2),rep("Overall",1)),
  Category = c("District","UHC","Kushtia","Dinajpur","November","Decmber","January","Yes","No","Overall"),
  Percentage = c(99.22,99.3,99.12,99.58,99.76,99.61,99.22,99.23,99.3,99.26),
  Lower_CI = c(98.97,99.04,98.9,99.31,65.07,99.37,98.91,99,98.1,99.08),
  Upper_CI = c(99.43,99.5,99.31,99.76,67.9,99.77,99.47,99.42,98.82,99.41),
  N = c(6000,5650,8095,3555,2874,4322,4338,6964,4686,11650)
)
kbl(registration,caption = "Completeness of Registration Number" , align = "c") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "middle")
```




```{r}
admission = data.frame(
  
  Variable = c(rep("Facility Type",2), rep("District",2),rep("Month",3), rep("Supervised",2),rep("Overall",1)),
  Category = c("District","UHC","Kushtia","Dinajpur","November","Decmber","January","Yes","No","Overall"),
  Percentage = c(98.46,99.09,98.42,99.55,100,100,100,98.53,99.11,98.76),
  Lower_CI = c(98.12,98.8,98.13,99.27,65.23,99.92,99.92,98.22,98.8,98.55),
  Upper_CI = c(98.76,99.32,98.68,99.74,68.06,1,1,98.8,99.36,98.96),
  N = c(5954,5638,8038,3554,2881,4339,4372,6915,4677,11592)
)
kbl(admission,caption = "Completeness of Date of Admission", align = "c") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "middle")

```




```{r}

timeadd = data.frame(
  
  Variable = c(rep("Facility Type",2), rep("District",2),rep("Month",3), rep("Supervised",2),rep("Overall",1)),
  Category = c("District","UHC","Kushtia","Dinajpur","November","Decmber","January","Yes","No","Overall"),
  Percentage = c(88.8,86.99,89.47,84.4,90.42,88.78,87.79,88.71,86.76,87.93),
  Lower_CI = c(87.98,86.1,88.78,83.17,68.8,87.8,86.78,87.95,85.76,87.32),
  Upper_CI = c(89.59,87.86,90.12,85.57,61.74,89.7,88.74,89.45,87.71,88.51),
  N = c(5370,4950,7307,3013,2605,3852,3838,6226,4094,10320)
)
kbl(timeadd,caption = "Completeness of Time of Admission", align = "c") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "middle")

```





```{r}

named = data.frame(
  
  Variable = c(rep("Facility Type",2), rep("District",2),rep("Month",3), rep("Supervised",2),rep("Overall",1)),
  Category = c("District","UHC","Kushtia","Dinajpur","November","Decmber","January","Yes","No","Overall"),
  Percentage = c(99.74,99.58,99.71,99.55,99.58,99.61,99.75,99.74,99.53,99.66),
  Lower_CI = c(99.57,99.37,99.56,99.27,64.95,99.37,99.55,99.59,99.3,99.54),
  Upper_CI = c(99.85,99.73,99.81,99.74,67.79,99.77,99.87,99.85,99.71,99.76),
  N = c(6031,5666,8143,3554,2869,4322,4361,7000,4697,11697)
)
kbl(named,caption = "Completeness of Name", align = "c") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "middle")
```



```{r}
aged = data.frame(
  
  Variable = c(rep("Facility Type",2), rep("District",2),rep("Month",3), rep("Supervised",2),rep("Overall",1)),
  Category = c("District","UHC","Kushtia","Dinajpur","November","Decmber","January","Yes","No","Overall"),
  Percentage = c(100,100,100,100,100,100,100,100,100,100),
  N = c(6047,5690,8176,3570,2881,4339,4372,7018,4719,11737)
)
kbl(aged,caption = "Completeness of Age", align = "c") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "middle")
```



```{r}
sexd = data.frame(
  
  Variable = c(rep("Facility Type",2), rep("District",2),rep("Month",3), rep("Supervised",2),rep("Overall",1)),
  Category = c("District","UHC","Kushtia","Dinajpur","November","Decmber","January","Yes","No","Overall"),
  Percentage = c(93.95,96.56,94.67,96.44,95.59,95.02,95.24,94.37,96.46,95.21),
  Lower_CI = c(93.32,96.05,94.17,95.78,62.27,94.33,94.57,93.8,95.89,94.81),
  Upper_CI = c(94.54,97.01,95.15,97.03,65.16,95.65,95.85,94.9,96.97,95.59),
  N = c(5681,5494,7732,3443,2754,4123,4164,6623,4552,11175)
)
kbl(sexd, caption = "Completeness of Sex",align = "c") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "middle")
```



```{r}
dist = data.frame(
  
  Variable = c(rep("Facility Type",2), rep("District",2),rep("Month",3), rep("Supervised",2),rep("Overall",1)),
  Category = c("District","UHC","Kushtia","Dinajpur","November","Decmber","January","Yes","No","Overall"),
  Percentage = c(97.8,96.4,96.72,98.04,97.85,96.91,96.91,98.01,95.8,97.12),
  Lower_CI = c(97.4,95.88,96.31,97.53,63.78,96.35,96.36,97.65,95.2,96.8),
  Upper_CI = c(98.16,96.87,97.1,98.47,66.65,97.41,97.4,98.32,96.36,97.42),
  N = c(5914,5485,7899,3500,2819,4205,4237,6878,4521,11399)
)
kbl(dist,caption = "Completeness of District", align = "c") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "middle")

```




```{r}
inve = data.frame(
  
  Variable = c(rep("Facility Type",2), rep("District",2),rep("Month",3), rep("Supervised",2),rep("Overall",1)),
  Category = c("District","UHC","Kushtia","Dinajpur","November","Decmber","January","Yes","No","Overall"),
  Percentage = c(19.51,1.56,14.13,3.22,16.94,9.26,8.33,17.07,1.5,10.81),
  Lower_CI = c(18.52,1.26,13.38,2.67,10.36,8.42,7.52,16.2,1.18,10.26),
  Upper_CI = c(20.54,1.92,14.9,3.85,10.27,10.17,9.18,17.97,1.89,11.39),
  N = c(1180,89,1154,115,488,402,364,1198,71,1269)
)
kbl(inve,caption = "Completeness of Investigation Done", align = "c") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "middle")

```



```{r}
care= data.frame(
  
  Variable = c(rep("Facility Type",2), rep("District",2),rep("Month",3), rep("Supervised",2),rep("Overall",1)),
  Category = c("District","UHC","Kushtia","Dinajpur","November","Decmber","January","Yes","No","Overall"),
  Percentage = c(69.03,74.11,69.84,75.27,71.82,70.78,72.44,69.75,74.08,71.49),
  Lower_CI = c(67.84,72.95,68.83,73.82,46.37,69.4,71.08,68.66,72.81,70.67),
  Upper_CI = c(70.19,75.25,70.84,76.67,49.37,72.13,73.76,70.82,75.33,72.31),
  N = c(4174,4217,5704,2687,2069,3071,3167,4895,3496,8391)
)
kbl(care,caption = "Completeness of Care Receivsed during admission", align = "c") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "middle")

```



```{r}
drug= data.frame(
  
  Variable = c(rep("Facility Type",2), rep("District",2),rep("Month",3), rep("Supervised",2),rep("Overall",1)),
  Category = c("District","UHC","Kushtia","Dinajpur","November","Decmber","January","Yes","No","Overall"),
  Percentage = c(81.48,93.39,84.9,92.63,85.7,88.08,87.85,82.46,94.38,87.25),
  Lower_CI = c(80.48,92.72,84.11,91.73,55.63,87.08,86.5,81.55,93.69,86.64),
  Upper_CI = c(82.45,94.02,85.67,93.47,58.61,89.03,88.8,83.34,95.02,87.85),
  N = c(44927,5314,6934,3307,2469,3822,3841,5787,4454,10241)
)
kbl(drug, caption = "Completeness of Drug receivsed during admission",align = "c") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "middle")


```




```{r}
diagno= data.frame(
  
  Variable = c(rep("Facility Type",2), rep("District",2),rep("Month",3), rep("Supervised",2),rep("Overall",1)),
  Category = c("District","UHC","Kushtia","Dinajpur","November","Decmber","January","Yes","No","Overall"),
  Percentage = c(61.5,79.26,64.52,82.91,70.77,71.12,69.56,63.89,79.36,70.11),
  Lower_CI = c(60.26,78.18,63.47,81.64,45.68,69.75,68.16,62.76,68.18,69.28),
  Upper_CI = c(62.73,80.3,65.55,84.13,48.68,72.47,70.92,65.02,80.51,70.94),
  N = c(3719,4510,5269,2960,2039,3086,3041,4484,3745,8229)
)
kbl(diagno, align = "c") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "middle")

```



```{r}
trt= data.frame(
  
  Variable = c(rep("Facility Type",2), rep("District",2),rep("Month",3), rep("Supervised",2),rep("Overall",1)),
  Category = c("District","UHC","Kushtia","Dinajpur","November","Decmber","January","Yes","No","Overall"),
  Percentage = c(68.46,83.04,71.43,84.9,79.76,76.35,72.67,71.79,81.1,75.53),
  Lower_CI = c(67.28,82.04,70.44,83.68,51.67,75.06,71.32,70.72,79.95,74.74),
  Upper_CI = c(69.63,84,72.41,86.06,54.67,77.61,73.98,72.84,82.2,76.3),
  N = c(4140,4725,5834,3031,2298,3313,3177,5038,3827,8865)
)
kbl(trt, caption = "Completeness of Final Diagnosis", align = "c") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "middle")


```


```{r}
all_i= data.frame(
  
  Variable = c(rep("Facility Type",2), rep("District",2),rep("Month",3), rep("Supervised",2),rep("Overall",1)),
  Category = c("District","UHC","Kushtia","Dinajpur","November","Decmber","January","Yes","No","Overall"),
  Percentage = c(12.02,0.74,8.75,1.51,9.82,6.04,5.12,10.5,0.68,6.55),
  Lower_CI = c(11.21,0.53,8.15,1.13,5.83,5.35,4.49,9.79,0.46,6.11),
  Upper_CI = c(12.87,1,9.39,1.97,7.33,6.79,5.82,11.24,0.96,7.01),
  N = c(727,42,715,54,283,262,224,737,32,769)
)
kbl(all_i, caption = "Completeness of All items", align = "c") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "middle")

```


```{r}

all_t= data.frame(
  
  Variable = c(rep("Facility Type",2), rep("District",2),rep("Month",3), rep("Supervised",2),rep("Overall",1)),
  Category = c("District","UHC","Kushtia","Dinajpur","November","Decmber","January","Yes","No","Overall"),
  Percentage = c(65.11,77.15,67.38,79.1,74.49,71.19,70.38,67.13,76.63,70.95),
  Lower_CI = c(63.89,76.04,66.35,77.73,48.15,69.82,69,66.01,75.39,70.12),
  Upper_CI = c(66.31,78.24,68.4,80.43,51.15,72.54,71.73,68.23,77.83,71.77),
  N = c(3937,4390,5503,2824,2146,3089,3077,4711,3616,8327)
)
kbl(all_t,caption = "Completeness of at least 10 items", align = "c") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "middle")


```

### Quality of care 

```{r}
spo = data.frame(
  Variable = c(rep("Facility Type",2), rep("District",2),rep("Month",3), rep("Supervised",2),rep("Overall",1)),
  Category = c("District","UHC","Kushtia","Dinajpur","November","Decmber","January","Yes","No","Overall"),
  Percentage = c(66.67,14.67,19.72,17.39,25,13.46,12.5,24.68,14.77,19.39),
  Lower_CI = c(38.38,9.42,13.52,4.95,16.37,5.58,2.66,15.56,8.11,13.66),
  Upper_CI = c(88.18,21.36,27.22,38.78,35.37,25.79,32.36,35.82,23.94,26.26),
  N = c(10,22,28,4,22,7,3,19,13,32)
)
kbl(spo,caption = "Quality of care SpO2(Oxygen)",  align = "c") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "middle")

```


```{r}
nspe= data.frame(
  
  Variable = c(rep("Facility Type",2), rep("District",2),rep("Month",3), rep("Supervised",2),rep("Overall",1)),
  Category = c("District","UHC","Kushtia","Dinajpur","November","Decmber","January","Yes","No","Overall"),
  Percentage = c(56.41,15,57.89,14.29,34.48,47.83,57.14,45.28,16.67,61.02),
  Lower_CI = c(39.62,3.21,40.82,3.04,17.94,26.82,18.4,31.56,0.42,47.44),
  Upper_CI = c(72.19,37.89,73.67,36.34,54.33,69.41,90.1,59.55,64.12,73.45),
  N = c(22,3,22,3,10,11,4,24,1,36)
)
kbl(nspe,caption = "Quality of care  Newborn Sepsis(Inj Antibiotics)", align = "c") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "middle")

```



```{r}
osneu= data.frame(
  
  Variable = c(rep("Facility Type",2), rep("District",2),rep("Month",3), rep("Supervised",2),rep("Overall",1)),
  Category = c("District","UHC","Kushtia","Dinajpur","November","Decmber","January","Yes","No","Overall"),
  Percentage = c(56.85,16.7,51.65,12.72,37.33,47.01,43.6,52.58,9.54,42.85),
  Lower_CI = c(53.37,13.03,48.45,9.07,43.1,14.68,24.92,49.38,6.38,40.08),
  Upper_CI = c(60.27,20.23,54.84,17.17,53.45,59.85,33.18,55.77,13.58,45.64),
  N = c(465,71,500,36,140,181,211,509,27,536)
)
kbl(osneu,caption = "Quality of care  Severe Pneumonia(oxygen)", align = "c") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "middle")



```


```{r}
ij =  data.frame(
  
  Variable = c(rep("Facility Type",2), rep("District",2),rep("Month",3), rep("Supervised",2),rep("Overall",1)),
  Category = c("District","UHC","Kushtia","Dinajpur","November","Decmber","January","Yes","No","Overall"),
  Percentage = c(38.75,47.34,39.26,50.18,50.93,43.64,33.26,41.63,42.05,41.73),
  Lower_CI = c(35.4,42.55,36.17,44.2,45.75,38.61,29.08,38.5,36.23,38.98),
  Upper_CI = c(42.19,52.17,42.41,56.15,56.1,48.75,37.66,44.81,48.04,44.52),
  N = c(317,205,380,142,191,168,161,403,119,522)
)
kbl(ij, caption = "Quality of care  Severe Pneumonia(Inj Antibiotics)",align = "c") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "middle")


```


### Adoption table

```{r}

adp =  data.frame(
  
  Variable = c(rep("Facility",4), rep("Facility type",2),rep("District",2),rep("Month",3),rep("Overall",1)),
  Category = c("Kustia DH","Kumarkhali UHC","Dinajpur DH","Hakimpur UHC","District","UHC","Kushtia","Dinajpur","November","Decmber","January","Overall"),
  Percentage = c(79.14,99.76,91.26,100,81.07,99.79,82.55,92.59,89.93,83.84,79.7,84.12),
  Lower_CI = c(77.88,99.14,89.08,0,79.96,99.25,81.47,90.72,88.41,82.21,77.93,83.18),
  Upper_CI = c(80.36,99.97,93.12,0,82.14,99.97,83.58,94.17,91.3,85.38,81.38,85.04)
)
kbl(adp,caption = " Adoption Table", align = "c") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "middle")

```


### Accuracy 


```{r}
cbc =  data.frame(
  
  Variable = c(rep("Facility",4), rep("Facility type",2),rep("District",2),rep("Month",3),rep("Overall",1)),
  Category = c("Kustia DH","Kumarkhali UHC","Dinajpur DH","Hakimpur UHC","District","UHC","Kushtia","Dinajpur","November","Decmber","January","Overall"),
  N.CBC = c(1616,594,517,2,2133,596,2210,519,814,978,917,2729),
 Percentage.CBC = c(77.36,95.19,95.92,100,81.16,95.21,81.46,95.93,81.48,83.95,86.27,83.81),
 N.Electrolyte = c(1856,623,532,2,2388,625,2479,534,942,1070,975,3013),
 Percenateg.Electrolyte = c(88.85,99.84,98.7,100,90.87,99.84,91.37,98.71,94.29,91.85,91.72,92.6)
)
kbl(cbc,caption ="Accuracy of CBC and Electrolyte" , align = "c") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "middle") %>% 
  add_header_above(c(" "," ", "CBC" = 2, "Electrolyte" = 2))

```



```{r}
blood =  data.frame(
  
  Variable = c(rep("Facility",4), rep("Facility type",2),rep("District",2),rep("Month",3),rep("Overall",1)),
  Category = c("Kustia DH","Kumarkhali UHC","Dinajpur DH","Hakimpur UHC","District","UHC","Kushtia","Dinajpur","November","Decmber","January","Overall"),
  "N" = c(2003,623,539,2,2542,625,2626,541,970,1128,1043,3167),
  "Percentage" = c(95.88,99.84,100,100,96.73,99.84,96.79,100,97.1,96.82,98.12,97.33),
  "N " = c(1622,600,523,2,2145,602,2222,525,837,981,911,2747),
  "Percenteg " = c(77.64,96.15,97.03,100,81.62,96.17,81.9,97.14,83.78,84.1,85.7,84.37)
)

kbl(blood,caption ="Accuracy of Blood Suger and Chest X-ray" , align = "c") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "middle") %>% 
  add_header_above(c(" "," ", "Blood Suger" = 2, "Chest X-ray" = 2))
```


```{r}
oxy=  data.frame(
  
  Variable = c(rep("Facility",4), rep("Facility type",2),rep("District",2),rep("Month",3),rep("Overall",1)),
  Category = c("Kustia DH","Kumarkhali UHC","Dinajpur DH","Hakimpur UHC","District","UHC","Kushtia","Dinajpur","November","Decmber","January","Overall"),
  "N" = c(1422,577,367,2,1789,579,1999,369,685,892,776,2368),
  "Percentage" = c(68.07,92.47,68.09,100,68.07,92.49,73.68,68.1,68.57,76.57,73,72.73),
  "N " = c(1697,503,447,2,2144,505,2200,449,384,953,891,2649),
  "Percenteg " = c(81.24,80.61,82.93,100,81.58,80.67,81.09,82.99,78.48,81.8,83.82,81.39)
)
kbl(oxy, caption ="Accuracy of Oxygen and IV fluid" ,align = "c") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "middle") %>% 
  add_header_above(c(" "," ", "Oxygen" = 2, "IV fluid" = 2))

```




```{r}
inj=  data.frame(
  
  Variable = c(rep("Facility",4), rep("Facility type",2),rep("District",2),rep("Month",3),rep("Overall",1)),
  Category = c("Kustia DH","Kumarkhali UHC","Dinajpur DH","Hakimpur UHC","District","UHC","Kushtia","Dinajpur","November","Decmber","January","Overall"),
  "N" = c(819,367,377,2,1196,369,1186,379,555,558,439,1565),
  "Percentage" = c(39.21,58.81,69.94,100,45.51,58.95,43.72,70.06,55.56,47.9,41.3,48.07),
  "N " = c(2077,615,536,2,2613,617,2692,538,994,1157,1052,3230),
  "Percenteg " = c(99.43,98.56,99.44,100,99.43,98.56,99.23,99.45,99.5,99.31,98.97,99.26)
)
kbl(inj,caption ="Accuracy of Injectable antibiotics and Inj Ampicilin" , align = "c") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "middle") %>% 
  add_header_above(c(" "," ", "Injectable antibiotics	" = 2, "Inj Ampicilin	" = 2))

```




```{r}
gen=  data.frame(
  
  Variable = c(rep("Facility",4), rep("Facility type",2),rep("District",2),rep("Month",3),rep("Overall",1)),
  Category = c("Kustia DH","Kumarkhali UHC","Dinajpur DH","Hakimpur UHC","District","UHC","Kushtia","Dinajpur","November","Decmber","January","Overall"),
  "N" = c(1876,573,538,2,2414,575,2449,540,909,1066,990,2989),
  "Percentage" = c(89.8,91.83,99.81,100,91.86,91.85,90.27,99.82,90.99,91.5,93.13,91.83),
  "N " = c(1841,570,388,2,2229,572,2411,390,852,1010,916,2801),
  "Percenteg " = c(88.13,91.35,71.99,100,84.82,91.37,88.87,72.09,85.29,86.7,86.17,86.03)
)
kbl(gen,caption ="Accuracy of Inj Gentamicin and Inj Ceftriaxone" , align = "c") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "middle") %>% 
  add_header_above(c(" "," ", "Inj Gentamicin	" = 2, "Inj Ceftriaxone	" = 2))


```




```{r}
newb=  data.frame(
  
  Variable = c(rep("Facility",4), rep("Facility type",2),rep("District",2),rep("Month",3),rep("Overall",1)),
  Category = c("Kustia DH","Kumarkhali UHC","Dinajpur DH","Hakimpur UHC","District","UHC","Kushtia","Dinajpur","November","Decmber","January","Overall"),
  "N" = c(2044,621,528,2,2572,623,2665,730,971,1148,1050,3195),
  "Percentage" = c(97.81,99.52,97.96,100,97.87,99.52,98.23,97.97,97.2,98.58,98.78,98.19),
  "N " = c(1930,623,479,2,2409,625,2553,481,927,1091,990,3034),
  "Percenteg " = c(92.39,99.84,88.87,100,91.67,99.84,94.1,88.91,92.79,93.6,93.13,93.24)
)
kbl(newb,caption ="Accuracy of Newborn Sepsis and Birth Asphyxia" , align = "c") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "middle") %>% 
  add_header_above(c(" "," ", "Newborn Sepsis	" = 2, "Birth Asphyxia" = 2))


```



```{r}
ref=  data.frame(
  
  Variable = c(rep("Facility",4), rep("Facility type",2),rep("District",2),rep("Month",3),rep("Overall",1)),
  Category = c("Kustia DH","Kumarkhali UHC","Dinajpur DH","Hakimpur UHC","District","UHC","Kushtia","Dinajpur","November","Decmber","January","Overall"),
  "N" = c(2003,624,533,2,2536,626,2627,535,969,1141,1026,3162),
  "Percentage" = c(95.88,100,98.89,100,96.5,100,96.83,98.89,97,97.94,96.52,97.17),
  "N " = c(1846,576,471,2,2317,578,2422,473,892,1031,951,2895),
  "Percenteg " = c(88.37,92.31,87.38,100,88.17,92.33,89.27,87.43,89.29,88.5,89.46,88.94),
  "n" = c(1971,622,535,2,2506,624,2593,537,966,1114,1025,3130),
  "Percent. "= c(94.35,99.68,99.26,100,95.36,99.68,95.58,99.26,96.7,95.62,96.43,96.19)
)
kbl(ref,caption = "Accuracy of Prematurity and LBW and Severe Pneumonia", align = "c") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "middle") %>% 
  add_header_above(c(" "," ", "Prematurity and LBW" = 2, "Severe Pneumonia" = 2,"Refer	" = 2))


```




